A programming model for temporal coordination (in music)

### 2014-05-06 paper/paper.tex
s/SonicPi/Sonic Pi and remove all unnecessary whitespace.

\newcommand{\lang}{SonicPi}

@@

\note{Introduction to SonicPi}

The underlying programming model of SonicPi provides a way to separate
the ordering of effects from the timing of
effects. Figure~\ref{three-chord-example} shows an example program
where three chords are played in sequence, combining simple notions of 
parallel, timed, and ordered effects.

@@

%
The \lang{} was previously discussed in~\cite{aaron2013sonic}

@@

\note{I suppose this is ok- I'm a bit wary about saying the simplification
takes less than $\epsilon$. It surely does, but I am only hand waving. 
We could time $e$ though in the model and show it is less than the schedule
time. We could go further and time the analogous parts of the SonicPi implementation
to check that the real $e$ is less than $\epsilon$. This would be good.}

>>>>

\newcommand{\lang}{Sonic Pi}

@@

\note{Introduction to Sonic Pi}

The underlying programming model of Sonic Pi provides a way to separate
the ordering of effects from the timing of
effects. Figure~\ref{three-chord-example} shows an example program
where three chords are played in sequence, combining simple notions of
parallel, timed, and ordered effects.

@@

%
\lang{} was previously discussed in~\cite{aaron2013sonic}

@@

\note{I suppose this is ok- I'm a bit wary about saying the simplification
takes less than $\epsilon$. It surely does, but I am only hand waving.
We could time $e$ though in the model and show it is less than the schedule
time. We could go further and time the analogous parts of the Sonic Pi implementation
to check that the real $e$ is less than $\epsilon$. This would be good.}
